---
output:
  bookdown::pdf_book:
    toc : no
    keep_tex: no
    number_sections: yes
header-includes:
    - \usepackage[utf8]{inputenc}
    - \usepackage{wrapfig}
    - \usepackage{lipsum}
---

Delineating spatial boundaries is one of the fundamental approaches in marine resource management and governance [@Song:2017iua]. Examples of such spatial delineation range from the designation of Exclusive Economic Zones (EEZs) to marine protected areas and fishing regulatory areas. As climate change re-shapes the distribution of marine biodiversity worldwide and living marine resources are expected to shift across the existing spatial boundaries, the effectiveness of current ocean management will be affected [@FredstonHermann:2018kp]. This dissertation centers around the challenges that climate change will bring to the management of marine fish stocks that straddle neighboring EEZs. Specifically, I look at how climate-induced shifts in marine species distributions will affect shared marine resources and the consequences for the dependent fishing communities. My main motivation for this work is to improve fisheries management in the light of the changing climate, highlighting the need for adaptive and cooperative management strategies. In this introductory chapter, I provide a brief history of the management of ‘shared stocks’ (e.g., fish stocks that cross international boundaries) in marine fisheries, followed by a summary of the impacts of climate change on the physical and chemical properties of the ocean and the consequences of these changes on marine life. Finally, I will review the existing knowledge about the management of shared stocks under climate change.

## Transboundary fisheries management 

From 1973 to 1982, members of the United Nations (UN) held a series of meetings to discuss regulations regarding the high seas, a region of international common property, at that time, consisting of waters from 12 nautical miles (22.22 km) from shore [@Munro:2004ug]. Among the main outcomes of these meetings was the establishment of the UN Convention on the Law of the Sea (UNCLOS). Under UNCLOS coastal states are allowed to claim special rights over the exploration and exploitation of marine resources up to 200 nautical miles (370 km) from their coasts. Area within which such special rights are claimed delineate the states’ Exclusive Economic Zone (EEZ) [@UnitedNations2018]. 

While intended to improve management of marine resources, including fisheries, by granting property rights of the resources to states through the designation of EEZ, the delineation of such resource management boundaries was not informed by biogeography of living marine resources. The natural distribution of marine species in time and space are not shaped by human actions but by the species’ contemporary biotic and abiotic factors and their evolutionary history [@Hutchinson:1957nt; @Nelson:2016kk]. In many cases, fish stocks distribute across EEZ boundaries; in view of this, UNCLOS created what we know today as shared fish stocks [@Munro:2002uf].

Generally speaking, shared fish stocks are those populations that move between different jurisdictions in the course of their life. The Food and Agricultural Organization (FAO) recognizes three types of shared stocks: (i) transboundary stocks are those that are shared between neighboring coastal nations e.g., Pacific halibut (*Hippoglossus stenolepis*) shared between Canada and the United States; (ii) straddling stocks are those that occur in two or more adjacent national jurisdictions and the high seas e.g., Chilean jack mackerel (*Trachurus murphyi*) off the coast of Chile and Peru but also the high seas; and (iii) highly migratory stocks are those that are found in the EEZs of coastal nations that are not necessarily adjoining, and the high seas (e.g., Bluefin tuna *Thunnus thynnus* migrates from the Mediterranean to the Gulf of Mexico) (Figure \ref{fig:SharedFigure}). The inception of the concept of "shared stocks" in fisheries management called for the establishment of new fisheries governance approaches and organizations. Many straddling and highly migratory stocks are managed by Regional Fisheries Management Organizations (RFMOs) [@MonllorHurtado:2017cm; @Song:2017va; @CullisSuzuki:2010fi]. At the EEZ level, transboundary stocks can be jointly managed by neighbouring countries under bi-lateral agreements, or managed unilaterally without legal-binding agreements with other countries.

The management of shared stocks is often viewed through the lens of game theory as a mean to analyze strategic interactions among decision-makers. Previous studies that apply game theory to study shared stocks have demonstrated that cooperation between nations in managing these stocks will most likely result in the best overall ecological and economic outcome for nations sharing a common resource [@Bailey:2010ga; @Eide:2013dha]. Lack of cooperation in managing shared stocks may result in over-exploitation [@Clark:1980js; @Nguyen:2018dk], reduce the profitability potential of the fishery [@Merino:2007jz], and led to conflict between coastal nations [@Spijkers:2017ij]. In some cases, when the target species is transboundary but sessile (e.g., clams) non-cooperation could provide a better overall solution [@Jensen:2015cf].

```{r SharedFigure, eval = T, fig.width = 9, fig.height = 4, echo=FALSE, fig.cap="Schematic representation of the different types of shared stocks as defined by the United Nations’ Food and Agriculture Organization (FAO). Adapted from FAO (http://www.fao.org/figis/servlet/IRS?iid=2665). Fish images from Dr. Seuss. 1960. One fish, two fish, red fish, blue fish. Penguin Random House LLC."}

# Optional figures http://www.fao.org/3/a0653e/a0653e04.htm 
# https://www.thedailystar.net/news-detail-219176

img <- readPNG("../Images/Intro_01.png")
grid.raster(img)
```


Forty years after the implementation of UNCLOS, the scale and status of all transboundary species and their fisheries in the world ocean is still not accurately characterized. Caddy (1997) estimated that there could be up to 1,500 transboundary fish species in the world. However, such estimation was not explicitly informed by the biogeography of marine species [@Caddy:1997ue]. More recently, Teh and Sumaila (2010) estimated that 206 exploited species could be considered shared stocks, accounting for a total catch of 34.2 million t and an estimated landed value of USD 30.7 trillion (in 2006 value). While the estimates by Teh and Sumaila (2010) are based on a literature review of shared species, the estimates likely represent the lower limit of the number of shared species and the scale of their fisheries because many shared species may not be reported in the literature. Particularly, recent research highlights the ecological and spatial interconnection of marine species [@Ramesh:2019va], suggesting that the number of shared species may be more than previous estimates. A bottom-up approach that estimate the number of shared stocks based on the biogeography of exploited marine species may thus be accurate. 

In Chapter 2 of this dissertation, using information from species’ biogeography, I aim to estimate the number of exploited marine species shared by neighboring countries and determine their contribution to global and regional catch and fisheries revenue. However, as climate change is causing a shift in the biogeography of marine species, it adds complexity in understanding and managing transboundary fisheries.

## Climate change and its effect on marine species

By 2017, greenhouse gas emissions from human activities is estimated to have warmed the Earth's surface by $1 \pm 0.2^ oC$ above pre-industrial levels and caused changes in ocean conditions [@IPCC:2018ws] (Figure \ref{fig:IPCC}).

<!-- # Load figure with LaTex this so it can be wraped with text -->
\begin{wrapfigure}{R}{.5\textwidth}  
 \begin{center}
    \includegraphics[width=.5\textwidth]{../Images/Intro_02.png}  
  \caption{Past and future changes in sea surface temperature, surface ocean pH and oxygen content (100-600 m depth). Adapted from IPCC (2019)} 
  \label{fig:IPCC}
\end{center}
\end{wrapfigure}

The ocean has absorbed 93% of heat produced from greenhouse gas emissions since 1970 [@Rheim:2013fv; @IPCC:2019tn]. As a consequence, global sea surface temperature (SST) has increased by 0.63$^o$C relative to 1850-1900 [@IPCC:2019tn]. Also, assessment by the Intergovernmental Panel on Climate Change (IPCC) has concluded that marine heatwaves have become more frequent [@Frolicher:2018dc], and ice sheets and glaciers have lost at an average rate of 220 $\pm$ 30 Gt $yr^{–1}$ of mass between 2006 and 2015 [@IPCC:2019tn]. The ocean has also sequestered about 30% of the carbon dioxide ($CO_{2}$) emissions from the atmosphere since the late 1980’s causing a pH decrease of 0.1 unit that corresponds to a 26% increase in acidity [@Ross:2011kd; @IPCC:2019tn]. Moreover, increasing stratification of oceanic waters, changes in ventilation and biogeochemistry has led to a 0.5 to 3.3% loss of oxygen content in the upper layer (1000 m) of the open ocean between 1970 and 2010. During the same period, oxygen minimum zones have expanded by 3 to 8% in volume [@IPCC:2019tn]. 

There are substantial regional variations in the $CO_{2}$-induced changes in ocean properties. For example, the Southern Ocean accounted for 35 to 43% of the total heat gain in the upper 2000 m layer of the global ocean between 1970 and 2017, and 25% of the global oxygen decline between 1970 and 1992 [@IPCC:2019tn]. Large reductions in oxygen have also been recorded for the north Pacific [@IPCC:2019tn]. In terms of pH, the largest declines between 1991 and 2011 were in the Indian Ocean (–0.027 units decade$^{ – 1}$), eastern Equatorial Pacific (–0.026 units decade$^{–1}$) and the South Pacific subtropical oceans (–0.022 units decade$^{–1}$) [@IPCC:2019tn].

Ocean properties are expected to continue to change in the $21^{st}$ century, although the intensity of these changes depends on the decisions’ society will take in the future in relation to carbon mitigation [@Gattuso:2015jz; @IPCC:2019tn]. The IPCC assessed the future climate using scenarios of greenhouse gas concentration in the atmosphere. These scenarios, known as Representative Concentration Pathways (RCPs), range from a "strong climate mitigation" (RCP 2.6) scenario to a "no mitigation" scenario where society has no effective greenhouse gases mitigation policies (RCP 8.5). Under RCP 2.6, radiative forcing increases 2.6 $W/m^2$ by 2100 relative to pre-industrial conditions while RCP 8.5 leads to a radiative forcing of 8.5 $W/m^2$ [@vanVuuren:2011cs; @Riahi:2011dk]. Under RCP 2.6, SST is projected to increase by 1.6$^o$C (CI[^Ipcc]: 1.1 - 2.0$^o$C) by 2031 - 2050 relative to 1850-1900, maintaining this trend (1.6$^o$C; CI: 0.9 - 2.4$^o$C) towards the end of the $21^{st}$ century. In contrast, following RCP 8.5 would result in an increase of 2$^o$C (CI: 1.5 - 2.4$^o$C) by 2031 - 2050 reaching 4.3$^oC$ (CI: 3.2 - 5.4$^o$C) by the end of the $21^{st}$ century relative to the same time period [@IPCC:2019tn]. In addition, the IPCC considers two intermediate scenarios, RCPs 4.5 and 6.0. While RCP 4.5 leads to a radiative forcing of 4.5 $W/m^2$ by 2100 relative to pre-industrial conditions and RCP 6.0 leads to 6.0 $W/m^2$ [@Thomson:2011iy; @Masui:2011gr]
<!-- , RCP 1.5 leads to a much lower radiative forcing, 1.9 $W/m^2$. The RCP 1.5 is a scenario that align most closely to aspired carbon mitigation level under the Paris Agreement of the United Nations Framework Convention on Climate Change [@IPCC:2019tn; @IPCC:2014bz].  -->
Here, I focus on RCP 2.6 and RCP 8.5 to capture the lower and upper range of climate change impacts on shared fish stocks and fisheries.

The ocean is projected to become warmer, less oxygenated with lower pH in the $21^{st}$ century relative to the present day (e.g., 1986-2005) under all RCPs [@IPCC:2019tn]. Specifically, by 2050, global mean SST is expected to increase by 0.65$^o$C (CI: 0.33 to 0.96$^o$C) under RCP 2.6 and 0.95$^o$C (CI: 0.60 to 1.29$^o$C) under RCP 8.5. The largest SST warming will be in the North Pacific, the tropical East Pacific, and in parts of the Arctic [@Gattuso:2015jz]. At the same time, surface pH will be reduced by -0.072 (CI: –0.072 to –0.072) units under RCP 2.6 and 0.108 (CI: –0.106 to –0.110) units under RCP 8.5, with the Arctic experiencing the largest decrease [@IPCC:2019tn; @Gattuso:2015jz]. Dissolved oxygen within the first 600 m will also be reduced by -0.9% (CI: -0,3 to -1.5) under RCP 2.6 and -1.4% (CI: –1.0 to –1.8) under RCP 8.5 [@IPCC:2019tn]. The subsurface layer of mid-latitude regions is prone to see the largest changes in dissolved oxygen [@Gattuso:2015jz]. By the end of the $21^{st}$ under RCP 8.5, ocean surface will be 3.2$^o$C warmer, –0.4 pH units lower, and have 3.9% less dissolved oxygen relative to the preindustrial level. In contrast, under RCP 2.6, ocean surface will be 1.2$^o$C warmer, pH will be –0.14 units lower and oxygen will be about 1% less than the preindustrial level [@IPCC:2019tn; @Gattuso:2015jz].

[^Ipcc]: In this case, the confidence interval used by the IPCC lies between the 17–83% probability range.


In responses to the changing ocean properties, marine species are changing their productivity, distribution, and penology [@Scheffers:2016gz]. The type and magnitude of the responses will vary depending on the oceanic region, taxonomic group and life history and ecological characteristics of the organisms [@Poloczanska:2016kk; @Gattuso:2015jz; @Scheffers:2016gz]. Changes in maximum sustainable yield (MSY) of 235 populations of 162 species are related to increasing water temperature. Between 1930 and 2010, MSY decreased by 4.1% (1.4 million tons) with some ecoregions (e.g., East Asian) experiencing losses of up to 35% [@Free:2019jq]. Future projections suggest that by the end of the $21^{st}$ century, 41 and 91% of global fish stocks will see a decline in MSY relative to 2012 under RCP 2.5 and 8.5 respectively [@Gaines:2018sg]. Moreover, shifting distributions has been the most widely documented response of marine species to ocean warming [@Poloczanska:2016kk; @Gattuso:2015jz]. Marine species, from phytoplankton to top-predator have shift their distribution ranges, mostly poleward, by an average of 72.0 $\pm$ 13.5 km per decade [@Poloczanska:2016kk]. These shifts are consistent with projections from species distribution models and are expected to continue in the $21^{st}$ century, even under a low emission scenario (RCP 2.6) [@Cheung:2010dt; @Barange:2014kr; @GarciaMolinos:2015fk]. Warming and less oxygenated waters have also contributed to changes in size of marine fishes [@Oke:2020hi; @Audzijonyte:2020hy]. Overall, fish body size is expected to decrease under a warming ocean [@Cheung:2012fo; @Pauly:2017hpa; @Pauly:2018hq] with variations between regions and species [@Audzijonyte:2020hy].

Shifts in exploited marine species abundance, distribution and penology will consequently impact the economics of fisheries [@Lam:2016dy; @Sumaila:2019ew; @Sumaila:2019gh] and food security [@Bell:2017hm; @Golden:2016gd] of communities that depend on them. It was estimated that in 2010, global fish landings were about 100 million tonnes (most of it destined to direct human consumption) generating about USD 150 billion [@Tai2017]. Estimates under RCP 8.5 suggest that global catches and revenue from fisheries could drop by 7.71 and 10.37%, respectively by 2050 with large regional differences [@Lam:2016dy]. For example, under RCP 8.5, the Exclusive Economic Zone (EEZ) of many tropical countries are expected to see >50% reductions in both catch and revenue [@Lam:2016dy]. This is the case of many Pacific Islands nations like the Philippines where fish represents a high proportion of animal-sourced food [@Asch:2018ca; @FAO:2018KK; @Bell:2017hm]. On the contrary, high latitude EEZs such as the Russian in the north and the Chilean in the south could see increases of up to 30% [@Lam:2016dy]. Similarly, societal vulnerability to climate change impacts on fisheries will not be the same across coastal communities. For example, indigenous fishing communities that rely on marine resources for food security and wellbeing are particularly vulnerable to climate change due to reduce access to resources [@Weatherdon:2016ws; @CisnerosMontemayor:2016gq]. Reducing greenhouse gas emissions to limit warming to a 1.5$^o$C increase by the end of the $21^{st}$ century (RCP 2.6) could increase fisheries catch potential by up to 30% [@Cheung:2016tt]. This would result in a USD 4.6 billion annual revenue increase benefiting 75% of coastal nations from which ~90% represent developing countries [@Sumaila:2019ew].

## Transboundary fisheries management under climate change

Current transboundary fisheries management might not be adapted to cope with shifts in species distributions under climate change [@Pinsky:2018cb, Chapter 4]. When a fish stock shifts from one EEZ to another due to climate change, fisheries in the states that lose the resource may opt for maximizing the exploitation of the fish stock. In contrast, the states that benefits from an increasing share of the fish stock may have more incentive to conserve it because of its increasing stake on the state's fisheries resources [@Diekert:2017fa]. As climate change continues to drive shifts in biogeography of exploited species, fish stocks are expected to expand into EEZs they did not occupy before while abundance will decrease in the lower latitudinal range of the species that can exacerbate conflicts over stock’s ownership and quota allocation [@Pinsky:2018cb; @Oremus:2020id]. Despite historical and projected changes in species distributions, today, many treaties concerning on the management of shared stocks are not well equipped to respond to stock shifts [@CullisSuzuki:2010fi; @Pinsky:2018cb, Chapter 4]. Specifically, some basic fisheries management strategies, such as quota allocations, are based on historical catch proportions, or species historical distribution, and could become outdated as species shift to cope with a changing ocean [@Pinsky:2014by; @Beaugrand:2011fd, Chapter 4]. Lack of or insufficient adaptation of management of shared stocks to the changing ocean conditions and species distributions will impact their effectiveness in ensuring the sustainability and benefits from the fisheries [@Sumaila:2020tp].

Both the magnitude and pattern of range shifts are important to characterize the risk and impacts of shifting shared stocks on transboundary fisheries management [@Pinsky:2012kq; @Link:2010ei]. The distribution of a fish stock can change in multiple ways. For example, the stock range can shift from one EEZ while approximately maintaining their range size. Also, the distribution of the stock can contract from or expand into a neighboring EEZ, resulting in a decrease or increase in range size, respectively (Figure \ref{fig:ShiftsFigure}). The magnitude and characteristics of range shifts of shared stocks will have different consequences to their management [@Link:2010ei]. Historically, such shifts have caused conflict between neighboring nations and compromised the sustainability of diverse shared stocks. Prominent examples include the 1980’s conflict over Pacific salmon between the United States (US) and Canada [@Miller:2004fpa; @Song:2017va].

```{r ShiftsFigure, eval = T, fig.width = 4, fig.height = 3, echo=FALSE, fig.cap="Schematic representation of different pattern of distribution shifts in shared stocks. Adapted from Link et al. (2010)"}

img <- readPNG("../Images/Intro_03.png")
grid.raster(img)
```


In addition to the magnitude and pattern of range shifts, it is important to understand the time frame at when the shifts and their impacts on fisheries will become apparent [@Pinsky:2014by; @Hawkins:2012hc]. The Special Report on the Ocean and Cryosphere in a Changing Climate used the concept of “Time of Emergence” (ToE) to discuss the challenge of changing ocean conditions, marine ecosystems and their challenges to ocean governance. As defined by the IPCC (adopted from Hawkins and Sutton, 2012), ToE is the moment in time when an anthropogenic change signal (e.g., future trend) rises above the background noise of natural variability (e.g., historical variation) [@IPCC:2019tn]. The premise behind ToE is that we can only be confident that a significant change has been detected when the signal of anthropogenic climate change is larger than the background of natural climate variability [@Hawkins:2012hc]. The concept of ToE has been extensively used to determine the time by which diverse oceanic variables (e.g., temperature, oxygen, CO2) will emerge in the global ocean [@Rodgers:2015jq; @Keller:2014jv; @Frolicher:2016dg; @Hawkins:2012hc; @Mahlstein:2011fy]. However, this concept has not been widely used on studies related to climate change and fisheries, until a recent study investigating the impacts of marine heatwaves in selected fisheries of the northeast Pacific [@Cheung:2020ja]. The concept ToE is useful to elucidate the impacts of climate change on transboundary fisheries and the consequences for their governance. For example, in the US, the arrival of the jumbo squid *Dosidicus gigas* to Washington state in 2009 created a new fishery under a *de facto* open access regime due to a lack of existing regulation. The time it took policy to be implemented was too long and the fishery was over-exploited [@Pinsky:2014by]. Moreover, since 2007 when Atlantic mackerel (*Scomber scombrus*) extended its distribution to Ireland's EEZ, the European Union (EU) and Norway, and Ireland have been in dispute over fishing rights and quota allocation [@Spijkers:2017ij].

## Research objectives


The goal of this dissertation is to understand the impacts of climate change on transboundary fish stocks and fisheries and their management, thereby informing international fisheries governance to prepare and respond to climate change. Specifically, my dissertation is guided by the following questions:

-	What are the existing transboundary species, and what is their importance to global fisheries in terms of catch and revenue?

-	How will climate change affect the distribution of shared stocks between neighbouring nations?

-	What are the consequences of climate change-driven distribution shifts to the management of transboundary species?

The dissertation is divided in three main data chapters and a conclusion chapter (Figure \ref{fig:DiagramFigure}). In Chapter 2, I present a global estimation of the current transboundary species and their importance to fisheries catches and revenue. Chapter 3 looks at the consequences that climate change will have to the management of shared stocks, more specifically, how the change in species distributions are going to affect the proportion of shared stocks between neighboring countries. In Chapter 4, I use two case studies of shared management between Canada and the United States to look at the policy implications of such shifts. Finally, in the conclusion chapter (Chapter 5), I provide an overall synthesis of the impacts of climate change to the management of shared stocks, not only highlighting the identified challenges informed by the previous chapters but also suggesting solutions to cope with a changing world. The methods of my dissertation are broadly based on numerical modeling and combination and synthesis of multiple datasets. In terms of modelling the methods relay on coupled species distribution models and Earth system models’ simulations to project future changes in transboundary species distribution in the $21^{st}$ century under two climate change scenarios.

```{r DiagramFigure, eval = T, fig.width = 8, fig.height = 4, echo=FALSE, fig.cap="Schematic diagram illustrating the structure of this dissertation. It starts with a global identification of transboundary species. It then proceeds to assess the climate change impacts on the identified species. Finally, it uses two case studies to explore the management implications of climate change to the joint management of transboundary species."}

img <- readPNG("../Images/Intro_04.png")
grid.raster(img)
```




<!-- # Recycled text -->

<!-- - Such shift is often related to stock depletion unless an agreement that compensates the loser by the winner is placed [@Sumaila].  -->

<!-- - In recent years the unmanaged fishery has seen its numbers substantially declined, probably due to lack of management or any precautionary approach [@Minsky:2014by]. These two questions are addressed in the third chapter of this dissertation and discussed more in depth on the fourth chapter using two case studies. -->