---
output:
  bookdown::pdf_book:
    toc: no
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
    latex_engine: xelatex
header-includes:
   - \usepackage{ragged2e}
   - \usepackage{setspace}
   - \usepackage{tocloft}
   - \usepackage{float} # Use the 'float' package
   - \floatplacement{figure}{H} # Make every figure with caption = h
   - \usepackage{wrapfig} # Wrap text over figure
   - \usepackage{pdfpages}
bibliography: ../References/Thesis_Ref.bib
csl: ../References/harvard.csl
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')

library(MyFunctions)

my_lib(
  c(
    # Introduction
    "png",
    "grid",
    # glossary
    "tidyverse",
    "knitr"
  )
)

```

<!-- Title page -->

```{r Cover, child = '../Sections/00_Cover.Rmd', eval = T}
```

<!-- Set numbers in non Arabic format. And starts in page II as required by G+PS.
NOTE: Remove normal markdown chapters before rendering to PDF  -->
\pagenumbering{roman}
\setcounter{page}{2}

<!-- # Committee form -->

```{r Committee_form, child = '../Sections/01_Committee_form.Rmd', eval = T}
```

\clearpage

<!-- Global page configuration -->

\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing

<!-- # Abstract -->

\section*{Abstract}
\addcontentsline{toc}{section}{Abstract} 

```{r Abstract, child = '../Sections/02_Abstract.Rmd', eval = T}
```

\clearpage

<!-- # Lay Summary -->

\section*{Lay Summary}
\addcontentsline{toc}{section}{Lay Summary}

```{r Lay_abstract, child = '../Sections/03_Lay_abstract.Rmd', eval = T}
```

\clearpage

<!-- # Preface -->

\section*{Preface}
\addcontentsline{toc}{section}{Preface}

```{r Preface, child = '../Sections/04_Preface.Rmd', eval = T}
```

\clearpage


<!-- Include a table of contents (including list of figures and tables) without numbering and with dots -->


\addcontentsline{toc}{section}{Table of Contents}

\thispagestyle{empty}
\begin{singlespace}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\setcounter{tocdepth}{3}
\tableofcontents
\clearpage
\addcontentsline{toc}{section}{List of Tables}
\listoftables
\clearpage
\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\clearpage
\end{singlespace}


<!-- # Glossary -->
\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}

```{r Glossary, child = '../Sections/05_Glossary.Rmd', eval = T}
```

\clearpage


<!-- # Acknowledgements -->
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

```{r Acknowledgements, child = '../Sections/06_Acknowledgments.Rmd', eval = T}
```

\clearpage

<!-- Remove page number  -->

\section*{Dedication}
\addcontentsline{toc}{section}{Dedication}

```{r Call_Niema, eval = T, fig.width = 7, fig.height = 8, echo=FALSE, fig.pos= "H"}

img <- readPNG("../Images/Niema_A.png")
grid.raster(img)

```

The only problem with dogs is that they do not live long enough.

\clearpage

# CHapter One: Introduction

<!-- Set Numbering properly for rest of the document -->
\pagenumbering{arabic}

<!-- This code will needs to be before each chapter so figures and tables numbering are according to each chapter -->
<!-- Note that the chapter number changes each time -->

\renewcommand{\thefigure}{1.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{1.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{1.\arabic{equation}}
\setcounter{equation}{0}

```{r Intro, child = '../Sections/07_Introduction.Rmd', eval = T}
```

\clearpage

<!-- From here on, include your different data chapters using normal Rmarkdown titles -->

# Chapter Two: The transboundary nature of the world’s exploited marine species

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{2.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{2.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{2.\arabic{equation}}
\setcounter{equation}{0}

```{r FishForVisa, child = '~/GitHub/FishForVisa/Scripts/Manuscript_Draft.Rmd', eval = T}
```

\clearpage

# Chapter Three: Early emergence of range shift-induced challenges in managing transboundary fish stocks under climate change

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{3.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{3.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{3.\arabic{equation}}
\setcounter{equation}{0}

```{r TransEmergence, child = '~/GitHub/TransEmergence/Scripts/Manuscript.Rmd', eval = T}
```

\clearpage

# Chapter Four: Challenges to transboundary fisheries management in North America under climate change

<!-- Set figure and table numbering according to the chapter -->
\renewcommand{\thefigure}{4.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{4.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{4.\arabic{equation}}
\setcounter{equation}{0}

```{r OC_Transboundary, child = '~/GitHub/OC_Transboundary/Ecol/Manuscript_Draft.Rmd', eval = T}
```

\clearpage

<!-- Done with data chapters, last sections -->

# Synthesis and Conclusion

```{r Conclusion, child = '../Sections/08_Conclusion.Rmd', eval = T}
```

\clearpage

<!-- # References -->
\section*{Bibliography}
\addcontentsline{toc}{section}{Bibliography} 

<!-- Reset page config. For proper referencing  -->
\noindent
\leftskip=2em
\parindent=-2em

<div id="refs"></div>

<!-- Go back to original page config. -->
\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing


<!-- # Appendices -->
\section*{Appendices}
\addcontentsline{toc}{section}{Appendices} 

<!-- ## Appendix A -->

\section*{Appendix A - Supplementary information for "The transboundary nature of the world’s exploited marine species"}
\addcontentsline{toc}{section}{Appendix A}

<!-- Set Figure, table and equations numbering according to the chapter -->
\renewcommand{\thefigure}{A2.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A2.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{A2.\arabic{equation}}
\setcounter{equation}{0}


```{r App_FishForVisa, child = '~/GitHub/FishForVisa/Scripts/supplements.Rmd', eval = T}
```


<!-- ## Appendix B  -->

\section*{Appendix B - Supplementary information for "Early emergence of range shift-induced challenges in managing transboundary fish stocks under climate change"}
\addcontentsline{toc}{section}{Appendix B}

<!-- Set Figure, table and equations numbering according to the chapter -->
\renewcommand{\thefigure}{A3.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A3.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{A3.\arabic{equation}}
\setcounter{equation}{0}


```{r App_TransEmergence, child = '~/GitHub/TransEmergence/Scripts/Supplements.Rmd', eval = T}
```

<!-- ## Appendix C -->

\section*{Appendix C - Supplementary information for "Challenges to transboundary fisheries management in North America under climate change"}
\addcontentsline{toc}{section}{Appendix C}


<!-- Set Figure, table and equations numbering according to the chapter -->
\renewcommand{\thefigure}{A4.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A4.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{A4.\arabic{equation}}
\setcounter{equation}{0}


```{r App_OC_Transboundary, child = '~/GitHub/OC_Transboundary/Ecol/Supplements.Rmd', eval = T}
```


<!-- END OF SCRIPT -->
