---
output:
  bookdown::pdf_book:
    toc : no
    keep_tex: no
    number_sections: yes
    fig_width: 6
    fig_height: 4
  # bookdown::word_document2
header-includes:
   - \usepackage{ragged2e}
   - \usepackage{setspace}
   - \usepackage{tocloft}
   - \usepackage{float} # Use the 'float' package
   - \floatplacement{figure}{H} # Make every figure with caption = h
   - \usepackage{wrapfig} # Wrap text over figure
bibliography: ../References/Thesis_Ref.bib
csl: ../References/harvard.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = 'allow')

library(MyFunctions)

my_lib(
  c(
    # Introduction
    "png",
    "grid",
    # glossary
    "tidyverse",
    "knitr"
  )
)

```

<!-- Title page -->

```{r Cover_Page, child = '../Sections/Cover.Rmd', eval = T}

### Status ###
# Drafted 19/07
# Done 20/07

```


<!-- Comitee form -->

```{r comitee_form, child = '../Sections/comitee_form.Rmd', eval = T}

```

\clearpage

<!-- Global page configuration -->

\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing


<!-- Set numbers in non arabic format. Remove normal markdown chapters before rendering to PDF  -->
\pagenumbering{roman}

<!-- # Abstract -->

\section*{Abstract}
\addcontentsline{toc}{section}{Abstract} 

```{r Abstract, child = '../Sections/Abstract.Rmd', eval = T}

```

\clearpage

<!-- # Lay Summary -->

\section*{Lay Summary}
\addcontentsline{toc}{section}{Lay Summary}

```{r Lay_Abstract, child = '../Sections/Lay_Abstract.Rmd', eval = T}

```

\clearpage

<!-- # Preface -->

\section*{Preface}
\addcontentsline{toc}{section}{Preface}

```{r Preface, child = '../Sections/Preface.Rmd', eval = T}

```

\clearpage


<!-- Include a table of contents without numbering and with dots :) -->
\thispagestyle{empty}
\begin{singlespace}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\setcounter{tocdepth}{3}
\tableofcontents
\listoffigures
\listoftables
\clearpage

\end{singlespace}


<!-- # Glossary -->
\section*{Glossary}
\addcontentsline{toc}{section}{Glossary}

```{r Acronyms, child = '../Sections/Acronyms.Rmd', eval = T}

```

\clearpage


<!-- # Acknowledgements -->
\section*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

```{r Acknowledgements, child = '../Sections/Acknowledgments.Rmd', eval = T}

### Status ###
# Pending
```

\clearpage

<!-- Remove page number  -->
\pagenumbering{gobble}

```{r Call_Niema, eval = T, fig.width = 7, fig.height = 8, echo=FALSE, fig.pos= "H"}

img <- readPNG("../Images/Niema_A.png")
grid.raster(img)

```

The only problem with dogs is that they do not live long enough

\clearpage

# Introduction

<!-- Set Numbering properly for rest of the document -->
\pagenumbering{arabic}

<!-- Set Figure and table numberring according to the chapter -->
\renewcommand{\thefigure}{1.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{1.\arabic{table}}
\setcounter{table}{0}

```{r Intro, child = '../Sections/Introduction.Rmd', eval = T}

### Status ###
# Drafted 19/08
# Revised W. 20/09
# Revised W. 09/11
# Done 11/11

```

\clearpage

# The transboundary nature of the world’s exploited marine species

<!-- Set Figure and table numberring according to the chapter -->
\renewcommand{\thefigure}{2.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{2.\arabic{table}}
\setcounter{table}{0}

```{r FishForVisa, child = '~/GitHub/FishForVisa/Scripts/Manuscript_Draft.Rmd', eval = T}

### Status ###
# Drafted 19/07
# Done 30/09
# Accepted for pub. 05/10


```

\clearpage

# Early emergence of range shift-induced challenges in managing transboundary fish stocks under climate change

<!-- Set Figure, table and equations numberring according to the chapter -->
\renewcommand{\thefigure}{3.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{3.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{3.\arabic{equation}}
\setcounter{equation}{0}

```{r TransEmergence, child = '~/GitHub/TransEmergence/Scripts/Manuscript.Rmd', eval = T}

### Status ###
# Drafted 27/09

```

\clearpage

# Challenges to transboundary fisheries management in North America under climate change

<!-- Set Figure, table and equations numberring according to the chapter -->
\renewcommand{\thefigure}{4.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{4.\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{4.\arabic{equation}}
\setcounter{equation}{0}

```{r OC_Transboundary, child = '~/GitHub/OC_Transboundary/Ecol/Manuscript_Draft.Rmd', eval = T}

### Status ###
# Drafted 10/03
# Done 20/07
# Accepted for pub. 25/09

```

\clearpage

# Synthesis and Conclusion

```{r Conclusion, child = '../Sections/Conclusion.Rmd', eval = T}

### Status ###
# Drafted 28/07
# Revised W. 09/11
# Revised W. 11/11
# Done 12/11


```

\clearpage

# References
<!-- \section*{References} -->

<!-- Reset page config. For proper referencing  -->
\noindent
\leftskip=2em
\parindent=-2em

<div id="refs"></div>

<!-- Go back to original page config. -->
\setlength{\parindent}{4em} 
\linespread{1}
\doublespacing


# Appendices

<!-- Set Figure, table and equations numberring according to the chapter -->
\renewcommand{\thefigure}{A2.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A2.\arabic{table}}
\setcounter{table}{0}

## Appendix A - Supplementary information for "The transboundary nature of the world’s exploited marine species"

```{r App_FishForVisa, child = '~/GitHub/FishForVisa/Scripts/supplements.Rmd', eval = T}

### Status ###
# Drafted 19/07
# Done 30/09
# Accepted for pub. 05/10


```

## Appendix B - Supplementary information for "Early emergence of range shift-induced challenges in managing transboundary fish stocks under climate change"

<!-- Set Figure, table and equations numberring according to the chapter -->
\renewcommand{\thefigure}{A3.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A3.\arabic{table}}
\setcounter{table}{0}


```{r App_TransEmergence, child = '~/GitHub/TransEmergence/Scripts/Supplements.Rmd', eval = T}

### Status ###
# Drafted 27/09

```

## Appendix C - Supplementary information for "Challenges to transboundary fisheries management in North America under climate change"

<!-- Set Figure, table and equations numberring according to the chapter -->
\renewcommand{\thefigure}{A4.\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A4.\arabic{table}}
\setcounter{table}{0}


```{r App_OC_Transboundary, child = '~/GitHub/OC_Transboundary/Ecol/Supplements.Rmd', eval = T}

### Status ###
# Drafted 10/03
# Done 20/07
# Accepted for pub. 25/09

```
